%
% Copyright (c) 2009-2010 LAAS/CNRS
% All rights reserved.
%
% Permission to use, copy, modify, and distribute this software for any purpose
% with or without   fee is hereby granted, provided   that the above  copyright
% notice and this permission notice appear in all copies.
%
% THE SOFTWARE IS PROVIDED "AS IS" AND THE AUTHOR DISCLAIMS ALL WARRANTIES WITH
% REGARD TO THIS  SOFTWARE INCLUDING ALL  IMPLIED WARRANTIES OF MERCHANTABILITY
% AND FITNESS. IN NO EVENT SHALL THE AUTHOR  BE LIABLE FOR ANY SPECIAL, DIRECT,
% INDIRECT, OR CONSEQUENTIAL DAMAGES OR  ANY DAMAGES WHATSOEVER RESULTING  FROM
% LOSS OF USE, DATA OR PROFITS, WHETHER IN AN ACTION OF CONTRACT, NEGLIGENCE OR
% OTHER TORTIOUS ACTION,   ARISING OUT OF OR IN    CONNECTION WITH THE USE   OR
% PERFORMANCE OF THIS SOFTWARE.
%
%                                             Anthony Mallet on Fri Jun 25 2010
%

\GenoM{} IDL is  independent of the programming language  used to implement the
services and internals  of a component. In order to  use the \GenoM{} generated
source code, it is necessary for  programmers to know how to access the service
parameters and ports from their programming languages. This chapter defines the
mapping of \GenoM{} IDL constructs to the supported programming languages.

The mapping between  \GenoM{} IDL and a programming  language diverges from the
OMG  CORBA standard.   This is  unfortunate, because  this might  lead  to some
confusion for the developers used to  OMG CORBA, but it was necessary to define
mappings well  targetting real-time platforms. The design  strategy that guided
the definition of those mappings was to try to have contiguous memory segments,
that do not  require memory management primitives, for most  of the data types.
Only unbounded string and sequences do not follow this scheme.

\GenoM{}  currently  implements  mappings  for   the  {\tt  C}  and  {\tt  C++}
languages.        For       the        {\tt       C}        language,       see
\xref[sec:mappings:c]{section~\ref{sec:mappings:c}}. For the {\tt C++}
language, see \xref[sec:mappings:cxx]{section~\ref{sec:mappings:cxx}}

\section{C mappings}
\label{sec:mappings:c}
\input{mappings-c}

\section{C++ mappings}
\label{sec:mappings:cxx}
\input{mappings-c++}
